In this dissertation, I have explored methods to leverage natural logic for extracting
  open domain knowledge from large-scale text corpora.
Unlike fixed-schema knowledge bases, this approach allows querying arbitrary facts.
Unlike open-domain knowledge bases -- such as Open Information Extraction approaches --
  this approach (1) does not limit the representation of facts to subject/relation/object
  triples; and (2) allows for rich inferences to be made so that we can find facts
  which are not only in the knowledge base, but also \textit{inferred} by some known
  fact.
From the other direction, unlike shallow information retrieval approaches, which also
  operate over large text corpora, the approach in this dissertation is robust to
  logical subtleties like negation and monotonicity.
We have applied this method to three areas: we have shown that we can predict the truth
  of common-sense facts with high precision and substantially higher recall than using
  a fixed knowledge base.
We have shown that we can segment complex sentences into short atomic propositions, and that
  this is effective for a practical downstream task of knowledge base population.
Lastly, we have shown that we can incorporate an \textit{evaluation function} encoding a
  simple entailment classifier, and that the hybrid of this evaluation function and
  our natural logic search is effective for question answering.

In \refchp{natlog} I reviewed the current theory behind natural logic as a logical formalism.
We reviewed a theory of denotations over lexical items, a notion of monotonicity over arguments
  to quantifiers and other functional denotations, and then introduced Monotonicity Calculus
  as a logic to reason over these monotonic functions.
We then introduced \textit{exclusion} to deal with antonomy and negation, and showed how we
  can extend Monotonicity Calculus to incorporate this additional expressive power.
Lastly, I introduced a brief sketch of a propositional natural logic, which would allow for
  jointly reasoning about multiple natural language utterances (for instance, the disjunctive
  syllogism).
I encourage future research into this propositional natural logic, and further research into
  the use of natural logic in place of conventional (e.g., first-order) logics for language
  tasks.

In \refchp{naturalli}, I introduce NaturalLI -- a large-scale natural logic reasoning engine
  for common sense facts.
I show that natural logic inference can be cast as a search problem, and that the \textit{join table}
  of \newcite{key:2008maccartney-natlog} can be more elegantly represented as a finite state
  machine we transition through during search.
I show that we can not only perform strictly warranted searches, but also learn a confidence for
  likely valid mutations; this allows the system to improve its recall by matching not only
  strictly valid premises, but also likely valid premises that it finds through the search.
I show that our system improves recall by 4$\times$ over lemmatized knowledge base lookup when
  assessing whether common-sense facts are true given a source corpus of 270 million unique
  short propositions.

In \refchp{openie}, I move from short propositions to longer sentences, and introduce a method for
  segmenting and trimming a complex sentence into the types of short utterances that NaturalLI can
  operate over.
This is done in two steps: First, complex sentences are broken into clauses, where each clause
  expresses one of the main propositions of the sentence (alongside potentially many additional
  qualifiers).
This is done by casting the problem as a search task: as we search down the dependency tree, each
  edge either corresponds to a split clause (possibly interpreting the subject / object of the
  governor as the subject of the dependent), or the search is told to stop, or the search is told
  to continue down that branch of the tree but not to split off that clause.
These clauses are then maximally shortened according to valid natural logic mutations to yield
  maximally informative atomic propositions.
These propositions can then either be used as propositions for a system like NaturalLI, or segmented
  further into OpenIE relation triples.
Using segmented triples from this system outperforms prior OpenIE systems on a downstream relation
  extraction task by 3 F$_1$.

In \refchp{qa}, we extend NaturalLI to operate over dependency trees and incorporate the method for
  creating atomic propositions from \refchp{openie} to allow NaturalLI to operate over a more complex
  premise set.
In addition, we introduce a method for combining a shallow entailment classifier with the more formal
  NaturalLI search.
At each step of the search, this classifier is run against a set of candidate premises; if any of these
  search states get close enough to a candidate premise according to the classifier, the fact is taken
  to be possibly true.
This behaves as a sort of evaluation function -- akin to evaluation functions in gameplaying algorithms --
  and allows for both (1) improving the recall of NaturalLI, and (2) creating a reasonable confidence
  value for likely entailment or contradiction even when the query cannot be formally proven or disproven.
I show that this method outperforms both strong IR baselines and prior work on answering multiple choice
  4\nth\ grade science exam questions.

There are a number of interesting and natural directions for future work in this area,
  which I will briefly discuss below:

\paragraph{Propositional Natural Logic} \refsec{natlog-propositional} sketches a simplistic propositional
  natural logic, based around a simple proof theory.
However, this is presented both without a formal proof of consistency or completeness, and without an
  associated model theory.
Furthermore, I have skirted issues of proper quantification and other first-order phenomena.
It would clearly be beneficial to the NLP community to have a natural logic which can operate over
  multiple premises, and more work in this area is I believe both useful and exciting.

\paragraph{Downstream Applications} This dissertation has presented a means of inferring the truth or
  falsehood of common-sense facts, but has only scratched the surface of downstream applications which
  can make use of this information.
There is I believe an interesting avenue of research which attempts to improve core NLP algorithms
  beyond what can be obtained with statistical methods by leveraging the common-sense knowledge acquired
  from large unsupervised text corpora.
For example, perhaps a parser which is more aware of facts about the world could correctly disambiguate
  prepositional attachments (e.g., \ww{I ate the cake with a fork / cherry}).

\paragraph{Natural Logic for Cross-Domain Question Answering}
The applications in this dissertation have focused on factoid-style true/false queries.
However, much of question answering is either (1) non-factoid (e.g., procedural) questions, or
  (2) requires finding a textual answer to the question (e.g., \ww{Who is the president of the US?)}.
Extending NaturalLI to handle these questions is a potential means of creating a truly cross-domain
  question-answering system.
If all premises are encoded in text, and all questions are given in text, then there is no notion of
  a schema or domain-specific model / named entity tag set / etc. which would limit the scope of questions
  that could be asked of the system.
For the first time, the same system could be asked both what color the sky is, and where Barack Obama was
  born.

I hope that this dissertation can inspire research in the direction of open-domain, broad coverage
  knowledge extraction, and encourage researchers to consider natural logic and its extensions
  as the foundation for storing and reasoning about this sort of knowledge.
As humans, we have chosen language as the means we store and represent knowledge, and I believe
  intelligent computers should do the same.


